The source code is divided into "src" directory containing source code related to the backend of CLup application and into "frontend" directory
which contains source code for the frontend of the CLup application.

\subsubsection{Backend}
Under the "src" directory, there are 5 important directories to mention alongside their usage in the application itself.
The controllers directory contains controllers that are responsible for processing incoming requests.
They invoke a business logic class to process business-related tasks.
The model directory is in charge of modeling the data and contains "dtos" and "entities" subdirectories.
DTOs (Data transfer objects) are used only to transfer data from one process or context to another.
Entities contain all objects that represent persistent data maintained in a database.
Repositories are used to decouple the business logic and the data access layers in the CLup application.
Services are used to implement the business logic of the CLup application. Each type of user has its service class.
Another important file in the src directory is the ApplicationConfiguration file in which different configurations have been defined.

\subsubsection{Frontend}
The frontend includes a lib directory where library instascan is provided.
Under src directory there exist a directory for each user type, which includes the functions to generate the view and to update the application state.
Inside the directory also there are files that define update and view logic of the whole app (actions such as login, logout are handled in those).
requests.ts include all the specifications for interacting with backend, while effects.ts include all the side-effects needed by the app.






