\subsection{Purpose}
% here we include the goals of the project

\subsubsection{Description of the Proposed System}
The project \"CLup - Customer Line up\" is a line spot reservation system that is planned to be used by managers, clerks and customers of many local vendors and chains.
The system aims to come up with a handy solution for the ongoing issue of proper social distancing management particularly in the matter of grocery shopping, by providing assistance to cope with the customer load for managers and helping customers access to products in a safe and controlled manner.

In particular, users will be able to see the locations, get a line number and book in advance for the grocery stores they would like to visit.
Once assigned a line number, the customer will be able to track the estimated time of arrival of the line as well as will wait for the notification that informs about his or her line's forthcoming arrival, hence waiting time in the line in the crowd is minimum.
Also, \"CLup\" provides uniquely generated QR codes per the line number, which can be utilized by the store managers as a proper monitoring tool in the entrances and exits of the locations.
All in all, the general purpose of the product is to keep the congestion levels in lines of the locations at minimum via providing useful features for all the users.


% TODO: All: Look at what @Ozan did for section 4 and complete the form by 11 Nov. Wednesday
% TODO: All: Does system notification use cases originate from another actor on use case diagrams? How are they modeled to users?
% TODO: @Ozan move new tables to LaTex
% TODO: @Hrvoje Check use case descriptions.

\subsubsection{Goals}

\begin{itemize}
    \item \textbf{$G_{1}$} Customers can issue a line number for a location.
    \item \textbf{$G_{2}$} Customers can issue line numbers for their future visits.
    \item \textbf{$G_{3}$} Customers can detail their visits by category and/or product.
    \item \textbf{$G_{4}$} Customers can plan their visit to the store. % Provide ETA, location and how much people are in the store.
    \item \textbf{$G_{5}$} Customers may prefer to use alternative time slots or partner stores for their visit.
    \item \textbf{$G_{6}$} Managers can prevent customers from issuing line numbers. % System stop, schedule system stop
    \item \textbf{$G_{7}$} Managers can customize the system to allow optimizations for increased granularity, flow control and time slot forecasting. % Settings, timeout
    % \item \textbf{$G_{8}$} Clerks can check in and check out customers' entrance and exit. % Would this count as a goal?
    \item % TODO: @Ozan Actual goal is to monitor customers
    \item \textbf{$G_{9}$} Customers can obtain printed line number tickets.
    % \item Customers can authenticate themselves using their e-mail address and password. % Not sure about involving A&A in goals.
\end{itemize}
% Manager:
% Set the estimated customer number to be in the location (based on govt. regulations, space availability etc.)
% Set the opening and closing hours of the store per day.
% Set the in-shop location & categories of products in the location
% Set the limit of reservation per customer per month, per day, per week
% Set the location of the store
% Add other chain members or partner stores
% Observe the current amount of customers in the location.
% Stop the system from issuing more tickets for a given day in case of an overflow or emergency
% Schedule a system stop.
% Set the timeout

% Clerk:
% Monitor the entrance and exit of customers with line numbers, by scanning their QR codes.
% Print line numbers with QR code on them for the physically arriving customers who doesn't have a virtual ticket.

% Customer:
% Retrieve a direct line number for a location
% Generate a QR code for entry
% See an ETA, like 30 mins are left for your line number
% View the location of the store to plan their trip
% Book a future line number for a day
% See the occupancy of the location for different time and day.
% View the alternative slot suggestions for the visit planned
% View the alternative slots available in near chain or partner stores
% Set the categories, products of interest before visit for finer granularity.
% Set the estimated time for visit.
% See the amount of people currently in the store
% Set user details, name, surname
% View forecasted occupancy for time slots.

% System:
% Forecast the occupancy of store per time slot
% Timeouts the line numbers when not registered for given timeout by manager.

% 80/20 percent split between bookings and physical appearence on domain assumptions for us to schedule in an easy way.
\subsection{Scope}

\subsubsection{Targeted Users}

CLup aims to resolve the problem of Customers queueing up in front of a location, without any control over the availability of place in the location and further contact tracing by the managers.
\\[0.5cm]
\textbf{Customer:} \\

Customers will be able to obtain specific line numbers for various locations using CLup, which they can track the estimated time available with and also view the location on a map application to plan their visit.
Customers can further obtain line numbers for future visits, based on the info provided by the system about the availability of free spots on the specific time intervals.
They may prefer to visit a different branch of the same chain.
Furthermore, they can provide specific products they intend to purchase or set an estimated time for their visit to allow finer granularity.
Some customers may also prefer to obtain a line number upon visiting the store physically.
To plan their visit in a time slot where the location will be less crowded, the users can see the occupancy of the location based on already taken line numbers and forecasts provided by the system.
\\[0.5cm]
\textbf{Clerk:} \\
The clerk ( which can be a shopping assistant or a security detail) can monitor the flow of customers and manually intervene in case of missing line numbers via performing manual checkout for a specific customer, or by printing line numbers physically for some customers.
\\[0.5cm]
\textbf{Manager:} \\

The location manager (which could be an actual manager, or someone responsible for handling customer management) can provide details regarding the availability of products and the location in general, by setting the opening hours, maximum allowed customers in shop, in-shop location of different products and categories, maximum amount of reservations that can be made per customer, line number timeout and the location.
Also, for chains and relevant stores, the manager can add chain members for the location.

\subsubsection{Relevant Phenomena}

\begin{table}[H]
    \begin{tabular}{|p{4cm}|p{4cm}|p{4cm}|}
        \hline
        \textbf{Phenomenon}    & \textbf{World / Machine}       & \textbf{Shared } \\ \hline
        Line Number & Machine & Yes \\ \hline
        Line Number Ticket & World & No \\ \hline
        Product & World & No \\ \hline
        Product Category & World & No \\ \hline
        In-store Location & World & Yes \\ \hline
        Occupancy Forecast & Machine & No \\ \hline
        Store & World & Yes \\ \hline
        Time Slot & Machine & Yes \\ \hline
        Ticket Printer & World & Yes \\ \hline
        Line Number Timer & Machine & No \\ \hline
        Customer Scheduling Algorithm & Machine & No \\ \hline
        % Line template:
        %          &               &  \\ \hline
    \end{tabular}
    \caption{Relevant Phenomena of CLup}
\end{table}

% here we include an analysis of the world and of the shared phenomena


% TODO: Self-note, let's discuss in meeting that DD and implementation is not far away

\subsection{Definitions, Acronyms, Abbreviations}
\subsubsection{Definitions}
\begin{itemize}
    \item \textit{Location}: the physical location of the business that operates the line reservation system
    \item \textit{Manager}: the user in charge of executive action within the location
    \item \textit{Customer}: the user with the goal of making a visit to the location
    \item \textit{Clerk}: the user in charge of handling the entrance and exit of customers
    \item \textit{Hard-coded Super User}: a single user that is used to create managers of locations administered by the software vendor
    \item \textit{Visit Time}: the time interval in which a customer performs a visit to the location
    \item \textit{Line Number}: A number that indicates the ordering of a specific customer in the line
    \item \textit{Line Number Ticket}: A physical ticket printed that features the line number and the QR code.
    \item \textit{Time Slot}: Specific intervals of time that are determined by the opening hours and average visit time per customer.
    \item \textit{Partner Store}: A different location that is included in the same beneficiary chain of command (such as another member of the franchise or store chain) or in a mutual agreement with the specific location
    \item \textit{Product}: Any item, items, service or services demanded by the customer, and provided by the location to the customer.
    \item \textit{In-store Location}: A location of a specific product or a product category inside the location.
    \item \textit{Working hours}: The time intervals that the store is open during each day.
    \item \textit{Maps API}: Google Maps API that is used as a mapping service %TODO: @Ozan remove Google Maps -> Maps
\end{itemize}
\subsubsection{Acronyms}
\begin{itemize}
    \item \textbf{RASD}: Requirement Analysis and Specification Document
    \item \textbf{QR Code}: Quick Response Code
    \item \textit{API}: Application Programming Interface
\end{itemize}
\subsubsection{Abbreviations}
\begin{itemize}
    \item \textbf{$G_n$}: $n^{th}$ goal
    \item \textbf{$D_n$}: $n^{th}$ domain assumption
    \item \textbf{$R_n$}: $n^{th}$ functional requirement
\end{itemize}
\subsection{Revision history}


\subsection{Reference Documents}
\begin{itemize}
    \item \href{https://beep.metid.polimi.it/documents/121843524/23d1869d-ab17-4e36-979e-f1ccbc59be24}{Specification Document: R\&DD Assignment AY 2020-2021}
    \item \href{https://standards.ieee.org/standard/29148-2011.html}{IEEE Std 830-1998: IEEE Recommended Practice for Software Requirements Specifications}
    \item \href{https://www.iso.org/standard/62021.html}{ISO/IEC 18004:2015 QR Code bar code symbology specification}
    \item \href{https://developers.google.com/maps/documentation/javascript/overview}{Maps API documentation}
\end{itemize}


\subsection{Document Structure}
This document is composed of six sections, each with the purpose described below: \\
\begin{itemize}
    \item \textbf{Introduction}: This section provides an introduction of the problem, the scope of the project with details regarding the goals, target users and phenomena.
        The goals of the project are formulated in accordance with the description of actions and actors in the Specification Document.
        Within the project's scope, properties and duties of different users and user groups are described in Target Users section.
        Furthermore, under the scope of the project, the relevant phenomena of the project is presented through their relevance to the world and the machine.
    \item \textbf{Overall Description}: This section builds upon the introduction section by providing expansion of the scope and relevant functionalities of the system.
        The basic perspective is provided considering the shared phenomena between the world and the system and the integrations of the system with other parties and products.
        The overall actions that can be conducted over the system is described using a detailed class diagram, portraying all required components of the system, their inner state and provided functionalities for other components to facilitate their purpose.
        All core features of the system is listed and explained using user scenarios to provide a better understanding of the real-world condition on which the use case should apply to, a state chart for demonstrating the relationship between various states the system can be in during the execution of the provided core feature scenario.
        Next, the requirements for the system to archive the aforementioned goals and allow the execution of the provided scenarios.
        The user characteristics, based on their roles in the system is further evaluated in this section, through the means of the needs that they have, how the system archives those needs via its requirements and goals.
        No system can be designed without a broad idea on what domain it exists in and how much the environment limits its ability to perform its features.
        Ergo, we provide the expected assumptions of the domain, the dependencies of the system to external components and the limits imposed by the world on the system.
    \item \textbf{Specific Requirements}: This section is the main section of the document.
        The external interfaces that the system requires to function correctly is presented with details and additional mockups if needed.
        The interfaces section is mainly concentrated on different views of user interfaces as the user-facing part is the main way to integrate with the system.
        In this section, functional requirements of the system are presented in detail, a common use case diagram is provided, and each use-case of the system is analyzed with details on a use case description table and a sequence diagram.
        The performance requirements of the system, with a focus on %TODO add when performance requirements are written
        The design constraints of the system, with a focus on different standard compliances, hardware limitations of the system to function and other constraints, like GDPR are also elaborated on this section.
        The vertical aspects that needs consideration are evaluated under the Software System Attributes subsection of this document, with an emphasis on Reliability, Availability, Security, Maintainability and Portability.

    \item \textbf{Formal Analysis Using Alloy}: This section features various models built and hypothesis verified using Alloy.
        This section demonstrates that some aspects of the requirements document can be formally proven to be correct and provides additional information about the proposed system to the engineers.
    \item \textbf{Effort Spent}: This section features the effort table, in which all team members provide a rough estimation on the time spent on creation of the various sections of the document.
    \item \textbf{References}: This section features different reference materials referred inside this document.
\end{itemize}
