% Here we include more details on all aspects in Section 2 if they can be useful for the development team.

\subsection{External Interface Requirements}

\subsubsection{User Interfaces}

% We need a tool, either stores raw content as text in our repo, or integrates with GitHub.
% TODO: Find the tool, maybe moqups? @Aydin
% TODO: @Ozan start ui mockups

% Actual mockups of user interfaces

\subsubsection{Hardware Interfaces}

% Do we integrate with external hardware?
\subsubsection{Software Interfaces}

% Do we integrate with custom software, expose an API?

\subsubsection{Communication Interfaces}


% What is a communication interface? the Internet? RF port? Radio? Bluetooth?

\subsection{Functional Requirements}
% Use draw.io, compatible with GitHub.
% TODO: @Roberto Use case diagram

% TODO: @Roberto finish the table and sequence diagrams
% Definition  of  use  case  diagrams,  use  cases  and  associated sequence/activity diagrams, and mapping on requirements

% Use case diagram

% For each use case:
%   Use case table
%   Use case sequence diagram

\subsubsection{Requirements}
\begin{itemize}
    \item \textbf{$R_1$} The system must allow users to authenticate using their e-mail address and password. % TODO: Roberto add use case
    \item \textbf{$R_2$} The system must allow customers to register using their e-mail address, their name, surname, phone number and a new password.
    \item \textbf{$R_{2.5}$} The system must provide a hard-coded super user to allow addition of locations and managers of locations. % TODO: Ozan write defn. of hard-coded and super user.
    \item \textbf{$R_3$} Managers must be able to add additional managers and clerks as users.
    \item \textbf{$R_4$} Managers must be able to set and update location specific information, that are maximum number of customers in the location at any given time, opening and closing hours of the store per each day, line number timeout, limit of reservation per customer on a predetermined time interval that is one of month, week or day, and location of the place % One form
    \item \textbf{$R_5$} Managers can add any other location as a partner store.
    \item \textbf{$R_6$} Managers can stop the system from issuing any more tickets for a given day
    \item \textbf{$R_7$} Managers can schedule the system stop for a future time.
    \item \textbf{$R_8$} Managers can set the in-shop locations for different categories and product items.
    \item \textbf{$R_9$} In case of a system stop, no further line numbers can be issued for the given time slots.
    \item \textbf{$R_{10}$} In case of a system stop, all line numbers in the stop time slots has to be cancelled.
    \item \textbf{$R_{11}$} The system must cancel those line numbers that the customer didn't arrive to the location for more than the set timeout interval.
    \item \textbf{$R_{12}$} In case of a ticket cancel, customer must be notified with an e-mail notification. % TODO: Roberto add use case
    \item \textbf{$R_{13}$} Clerks must register the entrance and exit of customers via scanning the QR code for their line number.
    \item \textbf{$R_{14}$} Clerks must be able to generate line number tickets in a printer compatible format.
    \item \textbf{$R_{16}$} Customers must be able to obtain a line number, except when the system is stopped or the store is full.
    \item \textbf{$R_{17}$} Customers must be able to obtain line numbers for different time slots in the future.
    \item \textbf{$R_{18}$} Customers can not obtain line numbers that exceed the quantity per time interval limits.
    \item \textbf{$R_{19}$} Customers can not obtain line numbers for time intervals that the system is stopped by a manager.
    \item \textbf{$R_{20}$} Customers must be able to see the estimated time available for their line number.
    \item \textbf{$R_{21}$} Customers must be able to set or update their phone number, password, name and surname. % TODO: Roberto add use case
    \item \textbf{$R_{22}$} Customers can select specific product and/or product categories they plan to visit in the location while obtaining a line number.
    \item \textbf{$R_{23}$} Customers can set an estimated time for their visit while obtaining a line number.
    \item \textbf{$R_{24}$} Customers must be able to view the shop location
    \item \textbf{$R_{25}$} Customers can view the occupation forecasts for the location at different time slots.
    \item \textbf{$R_{26}$} Customers can see the alternative suggestions for time slots while obtaining a line number for the future.
    \item \textbf{$R_{27}$} Customers can view the occupancy for the partner stores, if preferred time slot is not available while obtaining a line number.
    \item \textbf{$R_{28}$} Customers can view their line numbers with the number and the QR code.
    \item \textbf{$R_{29}$} The system must be able to provide a forecast for the occupancy of each location for any given time based on past visits.
\end{itemize}

% Goals, mapped to the requirements and domain assumptions they relate to
% (Requirements are vaguely given in Overview -> Product functions)
% (Domain assumptions are in Overview -> Assumptions,dependencies and constraints -> Domain Assumptions)
\subsection{Performance Requirements}

% Some basic stuff about how much users the system takes, speed etc...


\subsection{Design Constraints}

\subsubsection{Standards compliance}
% QR standard, UTC timing standard, GPS, etc...

\subsubsection{Hardware limitations}
% What needs to be on the phone?
\subsubsection{Any other constraint}
% GDPR regulations, local laws, etc...

% Isn't this similar to Overview -> Assumptions,dependencies and constraints -> Constraints?

\subsection{Software System Attributes}

\subsubsection{Reliability}

% Don't crash for long time, fault tolerance strategies like RAID, backups, etc

\subsubsection{Availability}

% 99.5% availability minimum, release any hardware control in case of power cut or unavailability.

\subsubsection{Security}

% Data hashing, salting, encryption of user data if necessary.

\subsubsection{Maintainability}

% Testing practices on all levels

\subsubsection{Portability}

% Usage of widely adopted platforms (Java, .NET, Browser), no custom protocol implementation apart from wide-spread
